\clearpage
\appendix
\renewcommand{\thetheorem}{4.\arabic{theorem}}
\setcounter{theorem}{0} 
\section{Proof of Theorem~\ref{the: static two-round}}

\label{sec:Proof of static two}


\begin{theorem} 
    Given any $\varepsilon > 0, \delta >0, n \in \mathbb{Z}_+, $ $U \in \mathbb{Z}_{+}$, $M \in \mathbb{Z}_{+}$, for any query $Q$ and any base shuffle-DP protocol $\mathcal{P}_Q$, our two-round protocol satisfies the following properties in the static setting:

    \begin{itemize}
    \item The messages received by the analyzer preserve $(\varepsilon,\delta)$-DP;
    \item The total error of this protocol is bounded by:
    \[
    \begin{aligned}
    &\mathrm{\gamma}_{\ell_p}\!\Big(
        Q,\;
        \frac{16}{\varepsilon}\ln\frac{2(\log M +1)}{\beta} \cdot m_{\max}(D)
    \Big)
    \\
    &+\;
    \err_{\ell_p}\!\Big(
        \mathcal{P}_Q,\;
        \frac{\varepsilon}{4m_{\max}(D)},\;
        \frac{\delta}{4m_{\max}(D)},\;
        \frac{\beta}{2},\;
        n\cdot 2m_{\max}(D)
    \Big)
    \end{aligned}
    \]



    \item In expectation, each user sends $1+ o(1)+\mathrm{Msg}(\mathcal{P}_Q, \allowbreak \frac{\varepsilon}{4m_{\max}(D)}, \allowbreak \frac{\delta}{4m_{\max}(D)}, \allowbreak n\cdot 2m_{\max}(D))$ messages.

\end{itemize}

\end{theorem}

\begin{proof}
    For privacy, the privacy budget $(\varepsilon, \delta)$ is split evenly between the $m_\tau$ estimation task and the query evaluation task. 
For the first round, invoking Lemma~\ref{lem: Bit Counting Protocol}, we have that for every $j \in \{0,1,2,\dots,\log M\}$, subdomain $[2^j+1,2^j]$ preserves $(\varepsilon/2,\delta/2)$-DP. Given that each $m_i$ only has an impact on a single subdomain $[2^j+1,2^j]$, 
parallel composition (Lemma~\ref{lem:Parallel Composition}) applies across the disjoint subdomains $\{[2^j+1,2^j]\}_{j\in\{0,1,2,\dots,\log M\}}$, ensuring this round satisfies $(\varepsilon/2,\delta/2)$-DP.
% it follows that the collection $\{[2^j+1,2^j]\}_{j\in\{0,1,2,\dots,\log M\}}$ preserves $(\varepsilon/2,\delta/2)$-DP by parallel composition (Lemma~\ref{lem:Parallel Composition}). 
For the second round, the protocol $\mathcal{P}_Q$ preserves $(\varepsilon/2,\delta/2)$-DP. Finally, by sequential composition (Lemma~\ref{lem:Sequential Composition}), our two-round protocol preserves $(\varepsilon,\delta)$-DP.
% please check that use lemma x.x or xx theory (lemma x.x)

For utility, let $Q(D)$ be the true query result on original dataset $D$, $Q(D^\tau)$ be the true query result on the standardized dataset $D^\tau$, and $\tilde{Q}(D^\tau)$ be our final noisy output. By the triangle inequality, the overall error $|\tilde{Q}(D^\tau) - Q(D)|$ can be decomposed into two parts:
$$|\tilde{Q}(D^\tau) - Q(D)| \le \underbrace{|Q(D^\tau) - Q(D)|}_{\text{Bias}} + \underbrace{|\tilde{Q}(D^\tau) - Q(D^\tau)|}_{\text{Noise}}.$$
\textit{Bounding the Bias}: 
% The bias is caused by users whose contribution $m_i$ exceeds $m_\tau$. 
The bias stems from the truncation of real records during the contribution standardization process. Let $m'$ denote the total number of records discarded from users with $m_i > m_\tau$. Since the bias $|Q(D^\tau) - Q(D)|$ is bounded by $\gamma_{\ell_p}( Q, m')$, our primary objective is to derive an upper bound for $m'$.
Let $C_j$ and $\tilde{C}_j$ denote the true and estimated number of users in the subdomain $I_j = [2^{j-1}+1, 2^j]$, respectively. Let $m_\tau = 2^l$. The algorithm selects $l$ as the largest index passing the threshold $T= \frac{2}{\varepsilon}\ln\frac{2(\log M +1)}{\beta}$. This implies that for all $j > l$, the estimated count $\tilde{C}_j$ did {not} pass the threshold, i.e., $\tilde{C}_j \le T$. 
Lemma~\ref{lem: Bit Counting Protocol} guarantees that for any such subdomain $I_j$ ($j > l$), with probability at least $1-\frac{\beta}{2(\log M +1)}$, the estimation error is bounded by $|\tilde{C}_j - C_j| \le T$. Combining these inequalities ($C_j \le \tilde{C}_j + |\tilde{C}_j - C_j|$), for any $j > l$, the true count is bounded by:
% Lemma~\ref{lem: Bit Counting Protocol} ensures that for any unselected subdomain $I_j$ ($j > l$), with probability at least $1-\frac{\beta}{2(\log M +1)}$, we have 
% \[
% |\tilde{C}_j-C_j| \le \frac{2}{\varepsilon}\ln\Big(\frac{2(\log M +1)}{\beta}\Big).
% \]
% Consequently, for any $j > l$, the true count is bounded by:
$$ C_j \le \frac{4}{\varepsilon}\ln\Big(\frac{2(\log M+1)}{\beta}\Big).
% = O\Big(\frac{1}{\varepsilon}\ln\frac{\log M}{\beta}\Big).
$$
Now, we calculate the total number of excluded records $m'$. A user in subdomain $I_j$ (where $j > l$) contributes at most $2^j$ records but is clipped to $m_\tau = 2^l$. The loss is at most $2^j - 2^l$.
Note that for $j > K = \lceil \log m_{\max}(D) \rceil$, the true count $C_j = 0$. Thus, summing over $j$ from $l+1$ to $K$:
$$\begin{aligned}
m'
&= \sum_{j=l+1}^{K} C_j \cdot (2^j - 2^l) \\
&\le \frac{4}{\varepsilon}\ln\frac{2(\log M +1)}{\beta} \cdot \sum_{j=l+1}^{K} (2^j - 2^l) \quad  \\
% &\le \frac{4}{\varepsilon}\ln(\frac{\log M+2}{\beta}) \cdot \sum_{j=l+1}^{K} 2^j \\
% &= \frac{4}{\varepsilon}\ln(\frac{\log M+2}{\beta}) \cdot (2^{K+1} - 2^{l+1})\\
% &\le \frac{4}{\varepsilon}\ln\frac{2(\log M +1)}{\beta} \cdot 4 m_{\max}(D)\\
% \\
% & = O\left(m_{\max}(D)\cdot\frac{1}{\varepsilon}\log\frac{\log M}{\beta}\right) 
&\le \frac{4}{\varepsilon}\ln\frac{2(\log M +1)}{\beta} \cdot 2^{K+1} \\
&\le \frac{16}{\varepsilon}\ln\frac{2(\log M +1)}{\beta} \cdot m_{\max}(D).
\end{aligned}$$
This explicitly validates the property (a) claimed in section~\ref{sec: static round 1}, confirming that the number of excluded records is bounded by $\tilde{O}(m_{\max}(D)/\varepsilon)$.
Consequently, the bias is bounded by: $$\mathrm{\gamma}_{\ell_p}\big(Q, \frac{16}{\varepsilon}\ln\frac{2(\log M +1)}{\beta} \cdot m_{\max}(D)\big).$$
with probability $1-\frac{\beta}{2}$ by union bound.



\textit{Bounding the Noise:} 
The noise magnitude depends on the threshold $m_\tau$. Specifically, the base protocol $\mathcal{P}_Q$ is invoked with privacy budget $(\frac{\varepsilon}{2m_\tau},\frac{\delta}{2m_\tau})$ and dataset size $n \cdot m_\tau$. To bound the noise, it suffices to prove that with high probability, $m_\tau \le 2m_{\max}(D)$.
Still using $K = \lceil \log m_{\max}(D) \rceil$, for any subdomain index $j > K$, the subdomain $[2^{j-1}+1, 2^j]$ strictly exceeds $m_{\max}(D)$, implying the true count $C_j=0$. By Lemma~\ref{lem: Bit Counting Protocol}, the estimated count $\tilde{C}_j$ is pure noise. Therefore, with probability at least $1-\frac{\beta}{2(\log M +1)}$, $\tilde{C}_j$ does not exceed the error bound $T$.
% please check if it exactly 1-beta/2
By union bound, with probability at least $1-\beta/2$, the algorithm will not select any $j > K$. Therefore, the selected threshold satisfies $m_\tau \le 2^K \le 2 m_{\max}(D)$.
{This confirms property (b).}
% By lemma~\ref{lem: Bit Counting Protocol}, if a subdomain $[2^{j-1}+1,2^j]$ is empty, i.e., $C_j=0$, with probability $1-\frac{\beta}{2(\log M +1)} $, the estimated count $\tilde{C}_j \le \frac{2}{\varepsilon}\ln \frac{2(\log M +1)}{\beta}$. Thus, by union bound, with probability at least $1-\beta/2$, for all $j> m_\tau$, $[2^{j-1}+1,2^j] $ is empty. Therefore, we can guarantee that with probability at least $1-\beta/2$, $m_\tau\le 2\cdot m_{\max}(D)$. As a result, the noise caused by $\mathcal{P}_Q$ is bounded by $\err_{\ell_p}(\mathcal{P}_Q,\frac{\varepsilon}{4m_{\max}(D)},\frac{\delta}{4m_{\max}(D)},\frac{\beta}{2},   n\cdot 2m_{\max}(D))$ with probability at least $1-\beta/2$. 
Substituting this bound into the error function, the noise is bounded by $\err_{\ell_p}(\mathcal{P}_Q,\frac{\varepsilon}{4m_{\max}(D)},\frac{\delta}{4m_{\max}(D)},\frac{\beta}{2}, n\cdot 2m_{\max}(D))$ with probability at least $1-\frac{\beta}{2}$.

Combining bias and noise yields the final error bound:
    \[
    \begin{aligned}
    &\mathrm{\gamma}_{\ell_p}\!\Big(
        Q,\;
        \frac{16}{\varepsilon}\ln\frac{2(\log M +1)}{\beta} \cdot m_{\max}(D)
    \Big)
    \\
    &+\;
    \err_{\ell_p}\!\Big(
        \mathcal{P}_Q,\;
        \frac{\varepsilon}{4m_{\max}(D)},\;
        \frac{\delta}{4m_{\max}(D)},\;
        \frac{\beta}{2},\;
        n\cdot 2m_{\max}(D)
    \Big)
    \end{aligned}
    \]
    with probability at least $1-\beta$.

    For the communication cost, recall that our protocol consists of two rounds, each consuming privacy parameters $(\varepsilon/2,\delta/2,\beta/2)$. 
    In the first round, each user executes the bit-counting protocol \(\mathcal{P}_{Q_\text{count}}\)~\cite{ghazi2021differentially} on each subdomain $I_j$ and parallel composition (Lemma~\ref{lem:Parallel Composition}) applies across the \(\log M+1\) disjoint subdomains.
    Crucially, since these subdomains are disjoint, each user contributes a value of $1$ to exactly one subdomain, which we denoted as $I^*$,  and $0$ to all remaining $\log M$ subdomains.
    According to Lemma~\ref{lem: Bit Counting Protocol}, the expected message cost for $I^*$ is $1 + O(\frac{\log(1/\delta)}{\varepsilon n})$, while when input value is $0$, the protocol only sends out $o(\frac{\log(1/\delta)}{\varepsilon n})$ message.
    Consequently, the total expected communication per user in the first round is:
    \[
        1 \cdot \Big(1 + O\big(\frac{\log(1/\delta)}{\varepsilon n}\big)\Big) + \log M \cdot O\big(\frac{\log(1/\delta)}{\varepsilon n}\big) = 1 + o(1),
    \]
    assuming $n \gg \log M \cdot \log(1/\delta)/\varepsilon$.
    % please check if this inequation is right
    
    % By lemma~\ref{lem: Bit Counting Protocol}, for each subdomain, the expected number of messages sent by a user is bounded by $1+O(\frac{\log (1/\delta)}{\varepsilon n}) = O(1)$. Since there are \(O(\log M)\) subdomains, the total communication per user in this round is $O(\log M)$. 
    In the second round, the base protocol \(\mathcal{P}_Q\) is executed on the standardized dataset with privacy budget $(\frac{\varepsilon}{2m_\tau},\frac{\delta}{2m_\tau})$. Thus, the communication cost is then $\mathrm{Msg}(\mathcal{P}_Q,\frac{\varepsilon}{2m_\tau},\frac{\delta}{2m_\tau},n\cdot m_\tau)$. From the utility analysis, we have \(m_\tau \le 2 m_{\max}(D)\), 
    % please check, with probability xx?
    and therefore this cost is bounded by $\mathrm{Msg}(\mathcal{P}_Q,\frac{\varepsilon}{4 m_{\max}(D)},\frac{\delta}{4 m_{\max}(D)},n \cdot 2m_{\max}(D))$. Combining these two rounds, the total number of messages per user is bounded by:
    $$1+o(1)+ \mathrm{Msg}(\mathcal{P}_Q, \allowbreak \frac{\varepsilon}{4m_{\max}(D)}, \allowbreak \frac{\delta}{4m_{\max}(D)}, n\cdot 2m_{\max}(D)).$$


\end{proof}

\section{Proof of Theorem~\ref{the: static one-round}}

\setcounter{theorem}{1}
\begin{theorem}
    Given any $\varepsilon > 0, \delta >0, n \in \mathbb{Z}_+, $ $U \in \mathbb{Z}_{+}$, $M \in \mathbb{Z}_{+}$, under the static setting, our one-round protocol achieves that:

    \begin{itemize}
    \item The messages received by the analyzer preserve $(\varepsilon,\delta)$-DP;
    \item The total error of this protocol is bounded by:
    \[
    \begin{aligned}
    &\mathrm{\gamma}_{\ell_p}\!\Big(
        Q,\;
        \frac{16}{\varepsilon}\ln\frac{2(\log M+1)}{\beta} \cdot m_{\max}(D)
    \Big)
    +\;
    O\Big(\err_{\ell_p}\!(
        \mathcal{P}_Q,\;    \\
    &
        \frac{\varepsilon}{m_{\max}(D)\cdot \log M},\;
        \frac{\delta}{m_{\max}(D)\cdot \log M},\;
        \frac{\beta}{\log M},\;
        n\cdot m_{\max}(D)
    )\Big)
    \end{aligned}
    \]



    \item In expectation, each user sends $1+o(1)+\sum_{j \in \{0,1,\dots, \log M\}} \allowbreak \mathrm{Msg}(\mathcal{P}_Q, \frac{\varepsilon}{2\cdot 2^j(\log M+1)}, \frac{\delta}{2\cdot 2^j(\log M+1)},n \cdot 2^j)$ messages.

\end{itemize}

\end{theorem}

\begin{proof}
     For privacy, the privacy budget $(\varepsilon, \delta)$ is split evenly between the $m_\tau$ estimation task and the query evaluation task.
    For the $m_\tau$ estimation,since the subdomains $\{I_j\}$ are disjoint, parallel composition (Lemma~\ref{lem:Parallel Composition}) guarantees that this step satisfies $(\varepsilon/2, \delta/2)$-DP.
    For query evaluation, by applying sequential composition (Lemma~\ref{lem:Sequential Composition}) over the $\lceil \log M \rceil + 1$ candidate query results, each with budget $(\frac{\varepsilon}{2(\log M+1)}, \frac{\delta}{2(\log M+1)})$, the total cost sums to $(\varepsilon/2, \delta/2)$-DP.
    By basic composition of these two parts, the overall protocol satisfies $(\varepsilon, \delta)$-DP.

    For utility, similar to the proof of Theorem~\ref{the: static two-round}, the total error is bounded by the sum of the clipping bias and the DP noise.
    Observe that the procedure for determining $m_\tau$ (including the privacy budget allocation and the threshold condition) is algorithmically equivalent to the first round of the two-round protocol. Consequently, the analysis for the number of excluded records holds directly. With probability at least $1-\beta/2$, the clipping bias is bounded by:
    \[
    \mathrm{\gamma}_{\ell_p}\!\Big(
        Q,\;
        \frac{4}{\varepsilon}\ln(\frac{2(\log M+1)}{\beta}) \cdot 4 m_{\max}(D)
    \Big)
    \]
    Regarding the selected threshold, the guarantee from Theorem~\ref{the: static two-round} remains valid: with probability at least $1-\beta/2$, we have $m_\tau \le 2m_{\max}(D)$.
    However, unlike the two-round protocol, the privacy budget for query evaluation is split among $\log M + 1$ candidate subdomains. For the selected query result corresponding to $m_\tau$, the base protocol $\mathcal{P}_Q$ is applied with parameters:
    \[
    \varepsilon' = \frac{\varepsilon}{2(\log M+1) m_\tau}, \quad \delta' = \frac{\delta}{2(\log M+1) m_\tau}, \quad n' = n \cdot m_\tau.
    \]
    Substituting the upper bound $m_\tau \le 2m_{\max}(D)$ into the error expression $\mathrm{Error}_{\ell_p}(\mathcal{P}_Q, \varepsilon', \delta', \beta', n')$, the noise is bounded by:
    \[
    \begin{aligned}
        O\Big( \mathrm{Error}_{\ell_p}\!\big(
        &\mathcal{P}_Q,\;
        \frac{\varepsilon} {m_{\max}(D) \cdot \log M},\;
        \frac{\delta}{m_{\max}(D) \cdot\log M},\; \\
        &\frac{\beta}{\log M},\;
        n \cdot m_{\max}(D)
    \big) \Big).
    \end{aligned}
    \]
    Combining the bias and noise bounds yields the final overall error bound.

For the communication cost, our one-round protocol executes two tasks in parallel: $m_\tau$ estimation and query evaluation across all candidate thresholds.

For the $m_\tau$ estimation task, the analysis is identical to the first round of the two-round protocol. Each user executes the bit-counting protocol $\mathcal{P}_{Q_\text{count}}$~\cite{ghazi2021differentially} on each subdomain $I_j$ with budget $(\varepsilon/2, \delta/2)$. Since the subdomains are disjoint, each user contributes a value of $1$ to exactly one subdomain and $0$ to all others. By Lemma~\ref{lem: Bit Counting Protocol}, the expected message cost is:
\[
1 \cdot \Big(1 + O\big(\frac{\log(1/\delta)}{\varepsilon n}\big)\Big) + \log M \cdot O\big(\frac{\log(1/\delta)}{\varepsilon n}\big) = 1 + o(1),
\]
assuming $n \gg \log M \cdot \log(1/\delta)/\varepsilon$.

For the query evaluation task, each user must send messages for all $\log M + 1$ candidate thresholds $\{2^j\}_{j=0}^{\log M}$. For each subdomain $j$, the user constructs a standardized dataset $D’$ of size $2^j$ and applies the base randomizer $\mathcal{R}_Q$ with privacy budget $(\frac{\varepsilon}{2 \cdot 2^j (\log M+1)}, \frac{\delta}{2 \cdot 2^j (\log M+1)})$ and participation size $n \cdot 2^j$. The communication cost for subdomain $j$ is therefore $\mathrm{Msg}(\mathcal{P}_Q, \frac{\varepsilon}{2\cdot 2^j(\log M+1)}, \frac{\delta}{2\cdot 2^j(\log M+1)}, n \cdot 2^j)$.

Summing over all $\log M + 1$ subdomains, the total expected communication per user is:
\[
1 + o(1) + \sum_{j=0}^{\log M} \mathrm{Msg}\Big(\mathcal{P}_Q, \frac{\varepsilon}{2\cdot 2^j(\log M+1)}, \frac{\delta}{2\cdot 2^j(\log M+1)}, n \cdot 2^j\Big).
\]

\end{proof}

   
\section{Proof of Theorem~\ref{the: dynamic setting guarantee}}

\renewcommand{\thetheorem}{5.\arabic{theorem}}
\setcounter{theorem}{0} 
\begin{theorem}
    Given any $\varepsilon > 0, \delta > 0$, any $T \in \mathbb{Z}_+$, and $n \in \mathbb{Z}_+$, $M \in \mathbb{Z}_+$, for any query $Q$, at all timestamps $t \in \{1, 2, \dots, T\}$ simultaneously, our protocol for the dynamic setting achieves the following guarantees:
\begin{itemize}
    \item The messages received by the analyzer preserve $(\varepsilon,\delta)$-DP;
    \item With probability at least $1-\beta$, the total error is bounded by:
    \[
    \begin{aligned}
    &O\Big(\gamma_{\ell_p}\big( Q, \frac{\log ^{1.5} T \cdot \log M}{\varepsilon} \ln \frac{T \cdot \log M}{\beta} \cdot m_{\max}(D^t)\big)\Big) + O\Big(\err_{\ell_p}\big(\mathcal{P}_Q,
    \\
    & \frac{\varepsilon}{m_{\max}(D^t) \cdot \log M}, \frac{\delta}{m_{\max}(D^t) \cdot \log M}, \frac{\beta}{\log M}, n \cdot m_{\max}(D^t)\big)\Big)
    \end{aligned}
    \]
    \item In expectation, each user sends $(\log M+1)(1+o(1)) + \sum_{j=0}^{\log M} \sum_{k=1}^{2^j} \mathrm{Msg}(\mathcal{P}_Q, \frac{\varepsilon}{2\cdot 2^j(\log M+1)}, \frac{\delta}{2\cdot 2^j(\log M+1)}, n \cdot 2^j)$ messages over the entire time horizon $T$.
\end{itemize}
\end{theorem}


\begin{proof}
    For privacy, the privacy budget $(\varepsilon, \delta)$ is split evenly between the two parallel tasks: dynamic counting and query evaluation, each receiving $(\varepsilon/2, \delta/2)$.

For \emph{dynamic counting}, the user participates in $\log M+1$ interval counting mechanisms. Since the intervals $\{I_j\}$ are disjoint (a user belongs to exactly one interval at any time), we apply parallel composition (Lemma~\ref{lem:Parallel Composition}) over the intervals, allocating budget $(\varepsilon', \delta') = (\frac{\varepsilon}{2(\log M+1)}, \frac{\delta}{2(\log M+1)})$ per interval.
Within each interval $j$, the binary mechanism operates over $\log T+1$ tree levels. By applying sequential composition (Lemma~\ref{lem:Sequential Composition}) over these levels, each level receives budget $(\frac{\varepsilon'}{\log T+1}, \frac{\delta'}{\log T+1})$.
Thus, dynamic counting satisfies $(\varepsilon/2, \delta/2)$-DP.

For \emph{query evaluation}, each user processes their data under all $\log M+1$ candidate thresholds. These thresholds are not disjoint (threshold $j+1$ covers threshold $j$), requiring sequential composition over the $\log M+1$ intervals with budget $(\varepsilon', \delta')$ per interval.
For each interval $j$, the user contributes $2^j$ streams, each running the base protocol with budget $(\frac{\varepsilon'}{2^j}, \frac{\delta'}{2^j})$. By composition over the $2^j$ streams, interval $j$ satisfies $(\varepsilon', \delta')$-DP.
Under the continual observation model~\cite{dwork2010continual,chan2011private}, incremental updates to streams incur no additional privacy cost, as the guarantee applies to the user's complete sequence $D_i = \{x_{i,t}\}_{t=1}^T$.
Thus, query evaluation satisfies $(\varepsilon/2, \delta/2)$-DP.

By basic composition of the two tasks, the overall protocol satisfies $(\varepsilon, \delta)$-DP.


For utility, similar to the static one-round protocol, the total error is bounded by the sum of clipping bias and DP noise.



\emph{Clipping Bias.}
Similar to the proof of Theorem~\ref{the: static two-round}, by Lemma ..., at each time $t$, the true count of interval $I_j$ is bounded by:
\[
C_j \le O(\frac{\log^{1.5} T}{\varepsilon'}\ln \frac{T}{\beta'}).
\]
Let $l = j^*$ and $K = \lceil \log m_{\max}(D^t) \rceil$. We can get the total number of discarded records is:
\[
\begin{aligned}
m'
&= \sum_{j=l+1}^{K} C_j \cdot (2^j - 2^l) \\
&\le O\Big(\frac{\log ^{1.5} T}{\varepsilon'} \ln \frac{T}{\beta'}\Big) \cdot \sum_{j=l+1}^{K} (2^j - 2^l) \\
&\le O\Big(\frac{\log ^{1.5} T \cdot \log M}{\varepsilon} \ln \frac{T\log M}{\beta}\Big) \cdot m_{\max}(D^t).
\end{aligned}
\]




\emph{DP Noise.}
For the selected threshold $m_\tau^t = 2^{j^*}$, the base protocol $\mathcal{P}_Q$ is applied with parameters:
\[
\varepsilon' = \frac{\varepsilon'}{2^{j^*}} = \frac{\varepsilon}{2(\log M+1) \cdot 2^{j^*}}, \quad \delta' = \frac{\delta}{2(\log M+1) \cdot 2^{j^*}}, \quad n' = n \cdot 2^{j^*}.
\]
Substituting the upper bound $2^{j^*} \le 2m_{\max}(D^t)$, the noise is bounded by:
\[
\begin{aligned}
    O\Big( \err_{\ell_p}\big( &\mathcal{P}_Q, \frac{\varepsilon}{m_{\max}(D^t) \cdot \log M}, \frac{\delta}{m_{\max}(D^t) \cdot \log M}, \\ &\frac{\beta}{\log M}, n \cdot m_{\max}(D^t)\big) \Big).
\end{aligned}
\]

Combining the bias and noise bounds yields the stated error guarantee.

For communication cost, the protocol executes two tasks in parallel: dynamic counting and query evaluation.

For \emph{dynamic counting}, each user runs $\log M+1$ independent binary mechanism instances (one per interval). 
Since intervals are disjoint, each user contributes to exactly one interval at any given time. 
By Lemma~\ref{lem: Bit Counting Protocol}, each binary mechanism instance with parameters $(\frac{\varepsilon'}{\log T+1}, \frac{\delta'}{\log T+1})$ sends $1 + o(1)$ messages in expectation.
Over $\log M+1$ intervals, the total cost is:
\[
(\log M+1) \cdot (1 + o(1)) = (\log M+1)(1+o(1)).
\]

For \emph{query evaluation}, the user maintains $\sum_{j=0}^{\log M} 2^j = 2^{\log M+1}-1$ streams across all intervals.
Each stream $S[j][k]$ runs an instance of the base protocol $\mathcal{R}_Q$ with budget $(\frac{\varepsilon'}{2^j}, \frac{\delta'}{2^j})$ and participant count $n \cdot 2^j$.
The communication cost for stream $S[j][k]$ is $\mathrm{Msg}(\mathcal{P}_Q, \frac{\varepsilon'}{2^j}, \frac{\delta'}{2^j}, n \cdot 2^j)$.
Summing over all streams:
\[
\sum_{j=0}^{\log M} \sum_{k=1}^{2^j} \mathrm{Msg}\Big(\mathcal{P}_Q, \frac{\varepsilon}{2\cdot 2^j(\log M+1)}, \frac{\delta}{2\cdot 2^j(\log M+1)}, n \cdot 2^j\Big).
\]

Combining both tasks, the total expected communication per user is:
\[
\begin{aligned}
    &(\log M+1)(1+o(1)) \\&+ \sum_{j=0}^{\log M} \sum_{k=1}^{2^j} \mathrm{Msg}\Big(\mathcal{P}_Q, \frac{\varepsilon}{2\cdot 2^j(\log M+1)}, \frac{\delta}{2\cdot 2^j(\log M+1)}, n \cdot 2^j\Big).
\end{aligned}
\]

\end{proof}